\thesistitle

### 2019-07-19 sections/conclusion.tex
Proposing new clone type definitions

\section{Future work} \label{sec:future_work}
This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated software metric refactoring. However, we scratched just the tip of the iceberg regarding all research opportunities in this field. In this section we describe possible extensions to this research, aswell as other research opportunities in this field of studies.

@@

\subsection{Identifying more types/definitions for clones}
In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known. We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entailed some decisions that have a large impact on the clones we considered for refactoring in this study.

Choosing different

@@

>>>>

\section{Future work} \label{sec:future_work}
This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring. However, we scratched just the tip of the iceberg regarding all research opportunities in this field. In this section we describe possible extensions to this research, as well as other research opportunities in this field of studies.

@@

\subsection{Identifying more types/definitions for clones}
In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known. We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.

\subsubsection{Type 2R clones}
With type 2R cl

@@

\subsubsection{Proposing new clone type definitions}
We think that current definitions of clone types still lack in the identification of all duplication issues that a developer should invest his/her refactoring efforts in. Current clone detection techniques still result in many false positives and false negatives. By proposing good definitions for code clones that mark the characteristics of harmful antipatterns, we can create more accurate suggestions to developers.
